Import_MetaData

### 2024-02-21 Code/Import_MetaData.Rmd
Added missing data and reprocessed run #78. Regnerated GAM and plots

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataOut <- file.path("..","Data")
ProjectRows <- c("MiSa|JuNa|SaAr")
ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")

>>>>

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataOut <- file.path("..","Data")
ProjectRows <- c("MiSa|JuNa|SaAr|MaBe|LaGe")
ProjectCols <- c("PrimaryOperator", "SampleID", "Run", "Strain", "ExpCul", "ExpDate", "ExpStartTime", "Par_ue", "Photoperiod", "Temp_c", "MC", "Tube","O2", "O2_Category", "WL","LightShape", "Optode","OptodeCh","OptodeMeasure", "ExpEndDate")
